\textbf{\Large Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}

### 2024-02-21 supplementary_BiSC_outdoor_AP.tex
Updates from Overleaf

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Tittle of the paper --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{\large Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% --- Tittle of the paper --- %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{\Large Supplementary materials: Development of outdoor air pollution models for estimating exposure in the Barcelona Life Study Cohort (BiSC)}}

@@

\vspace*{-1cm}
